\LARGE \bf Mean Estimation from Adaptive One-bit Measurements

### 2017-10-01 Writeups/onebit_adaptive_Allerton_V3.tex
another minor edit to Section III

\title{\LARGE \bf Mean Estimation from Adaptive One-bit Measurements}
%
\author{
\IEEEauthorblockN{Alon Kipnis}
\IEEEauthorblockA{Department of Electrical Engineering \\
Stanford University\\
Stanford, CA\\}
\and
\IEEEauthorblockN{John C. Duchi}
\IEEEauthorblockA{Department of Electrical Engineering \\
and Department of Statistics \\
Stanford University\\
Stanford, CA\\}
}

@@

\section{Relation to Remote Multiterminal Source Coding \label{sec:ceo}}
In this section we draw a connection between our general problem of mean estimation from one-bit samples and the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem. The setting of the CEO includes $n$ encoders, each has access to a noisy version of a random source sequence. 
% $\left\{ U_j,\,j=1,2,\ldots \right\}$. 
The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. \par
Assuming that $\theta$ is drawn once from the prior $\pi(\theta)$, mean estimation from one-bit under distributed encoding (setting (iii) in the Introduction) corresponds to the Gaussian CEO setting with block length $k=1$, where the $i$th encoder observes
\begin{equation}
\label{eq:Gaussian_channel}
X_i = \theta + \sigma Z_i,
\end{equation}
with $Z_1,\ldots,Z_n$ i.i.d. standard normal, and uses $R_i=1$ bits to transmit its observation. As a result, the quadratic distortion in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$ and Gaussian observation noise at each estimate of variance $\sigma^2$, provides a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting. Note that the difference between the Gaussian CEO and our setting is in the fact that each encoder may use an arbitrarily large blocklength $k$, thus describing $k$ realizations of $\theta$ using $k$ bits, whereas our setting only allows $k=1$. 
 \\

>>>>

\title{\LARGE \bf Mean Estimation from Adaptive One-bit Measurements}
%
\author{
\IEEEauthorblockN{Alon Kipnis}
\IEEEauthorblockA{Department of Statistics \\
Stanford University\\
Stanford, CA\\}
\and
\IEEEauthorblockN{John C. Duchi}
\IEEEauthorblockA{Department of Electrical Engineering \\
and Department of Statistics \\
Stanford University\\
Stanford, CA\\}
}

@@

\section{Relation to Remote Multiterminal Source Coding \label{sec:ceo}}
In this section we draw a connection between our general problem of mean estimation from one-bit samples and the remote multiterminal source coding problem \cite{berger1996ceo}, also known as the CEO problem. The setting of the CEO includes $n$ encoders, each has access to a noisy version of a random source sequence. 
% $\left\{ U_j,\,j=1,2,\ldots \right\}$. 
The $i$th encoder observes $k$ noisy source symbols and transmit $R_i k$ bits to a central estimator. \par
Assuming that $\theta$ is drawn once from the prior $\pi(\theta)$, our mean estimation problem from one-bit samples under distributed encoding (setting (iii) in the Introduction) corresponds to the Gaussian CEO setting with $k=1$ source realization: the $i$th encoder uses $R_i=1$ bits to transmit a message that is a function of $X_i = \theta + \sigma Z_i$, where $Z_i$ is standard normal. As a result, the MSE in the optimal source coding scheme for the CEO with $n$ terminals at rates $R_1 = \ldots = R_n = 1$, a Gaussian observation noise at each estimate of variance $\sigma^2$, and an arbitrary number of $k$ independent draws of $\theta$, provides a lower bound on the MSE distortion in estimating $\theta$ in the distributed encoding setting. Note that the difference between the CEO and ours is in the fact encoders in the CEO describe $k$ realizations of $\theta$ using $k$ bits with MSE averaged over these realization, whereas our setting only allows $k=1$. 
 \\
